```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("pls", "plsr")`

## Tuning Parameters

```{r}
#| label: plsr-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = "num_comp",
                 default = "2L")

param <-
  pls() |> 
  set_engine("plsr") |> 
  set_mode("regression") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: plsr-param-list
#| echo: false
#| results: asis
param$item
```


## Translation from parsnip to the underlying model call (regression)

`r uses_extension("pls", "plsr", "regression")`

```{r}
#| label: plsr-reg
library(plsmod)

pls(num_comp = integer(1), predictor_prop = double(1)) |>
  set_engine("plsr") |>
  set_mode("regression") |>
  translate()
```

[plsmod::pls_fit()] is a function that: 

 - Converts the predictors and outcomes to matrices.
 - Determines the number of predictors in the data.
 - Adjusts `num_comp` if the value is larger than the number of factors.

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-zv.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## References

 - Mevik BH, and Wehrens R (2007). "The pls package: principal component and partial least squares regression in R." Journal of Statistical software, 18, 1-23. 
 
